### 2016-07-15 intro.tex
cheers

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; \jnote{I think this is also reasonable; typically
security is defined without regard for efficiency} \tsnote{My
complaint isn't about efficiency. It's about the fact that, by not
including $|M|$ in the definition, the trivial scheme I give (just
below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!}
\tsnote{Okay, well then we need some way to ``rule out'' the trivial
solution. Perhaps just in the text -- yes, the trivial scheme works,
but it isn't interesting in practice. Also, in the concrete security
bounds that we will prove, the size of the representation is going
to come up, e.g.\ the number of bits in the BF array directly affect
the FP rate. Hence it makes sense to say things like ``an
$(n,k,m)$-filter\ldots'' where $m$ is the size of the
representation.} \jnote{I still disagree: efficiency is orthogonal
to functionality and security.} The surrounding text does say that
$\mathbf{B}_1$ ``outputs a compressed representation [of
$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
means is never addressed. The formal syntax admits
$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints. But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

>>>>

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; \jnote{I think this is also reasonable; typically
security is defined without regard for efficiency} \tsnote{My
complaint isn't about efficiency. It's about the fact that, by not
including $|M|$ in the definition, the trivial scheme I give (just
below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!}
\tsnote{Okay, well then we need some way to ``rule out'' the trivial
solution. Perhaps just in the text -- yes, the trivial scheme works,
but it isn't interesting in practice. Also, in the concrete security
bounds that we will prove, the size of the representation is going
to come up, e.g.\ the number of bits in the BF array directly affect
the FP rate. Hence it makes sense to say things like ``an
$(n,k,m)$-filter\ldots'' where $m$ is the size of the
representation.} \jnote{I still disagree: efficiency is orthogonal
to functionality and security.} \fixme{
Let's discuss this verbally, because I feel like we are talking past each other.}The surrounding text does say that
$\mathbf{B}_1$ ``outputs a compressed representation [of
$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
means is never addressed. The formal syntax admits
$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints. But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.
